Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Formatting
Wording

A global cardinality constraint \cite{globCard} is then imposed on the array $\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e. $\{0 .. n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 .. 1\}$) and once only (i.e. $\{1 .. 1\}$). The $\state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on). These criteria are imposed on the $\state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.

The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule. The $\state$ array is presented as coloured boxes, and below that the $\timeSlot$ array. The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The $\state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE. The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened. To the right of the schedule is schema for the dfa. Coloured arc represent a transition from one state to another. The dfa is encoded as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$ where a transition is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we specify the accepting states, being all states except the start state (white) and bye state (pink).

>>>>

A global cardinality constraint \cite{globCard} is then imposed on the array
$\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all
other skippers (i.e. $\{0 \ldots n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 \ldots
1\}$) and once only (i.e. $\{1 \ldots 1\}$). The $\state$ variables are then used
to impose match race criteria 4 (if last in flight $i$ then not first in flight
$i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$)
and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In
addition, we have the rule that if a skipper has finished his matches in flight
$i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on).
These criteria are imposed on the $\state$ variables via a deterministic finite
automata (DFA) constraint \cite{Pesant04}.

The constraints above are shown pictorially in Figure~\ref{skipper5}, and
corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
is presented as coloured boxes, and below that is the $\timeSlot$ array. The
arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
$\state$ array is coloured with green representing LAST, yellow for MID, blue
for FIRST, red for LAST and (not shown) pink for BYE. The schedule of
Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
the right of the schedule is schema for the DFA. Coloured arcs represent a
transition from one state to another. The DFA is encoded as a set of transition
objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
specify the accepting states, which are all states except the start state
(white) and the bye state (pink).
